Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-04 paper/paper.tex
outline and table

%\paragraph{Outline} We give details of our new algorithm in
%Sec.~\ref{sec:algorithm}.

@@

\section{C-}
We use a fragment of C as our underlying logic.  We will refer to this fragment
as C-.  The characteristic property of C- is that safety can be decided for
C- programs by using a bounded model checker.  A C- program is just a C program
with the following syntactic restrictions:

@@

\section{Experimental Results}

@@

\begin{figure}
\begin{center}
\begin{tabular}{l|l|l|l|l}
Problem & {\sc Brahma} & {\sc Kalashnikov} & {\sc Kalashnikov} & {\sc Kalashnikov} \\
        &               &                    & (no width)         & (CBMC only) \\
\hline
p1 & 3.20s &{\bf 1.83s} &23.54s &8.07s \\
p2 & 3.60s &{\bf 1.49s} &1271.12s &8.19s \\
p3 & {\bf 1.40s} &1.60s &4.09s &5.90s \\
p4 & 3.30s &{\bf 1.86s} &79.72s &8.15s \\
p5 & 2.20s &{\bf 1.98s} &12.16s &8.10s \\
p6 & 2.40s &{\bf 1.51s} &104.19s &8.17s \\
p7 & {\bf 1.00s} &4.04s &- &14.49s \\
p8 & {\bf 1.40s} &4.31s &- &14.20s \\
p9 & {\bf 5.80s} &35.09s &505.10s &13.45s \\
p10 & 76.10s &{\bf 9.80s} &- &19.14s \\
p11 & 57.10s &{\bf 9.40s} &{\bf 9.40s} &32.98s \\
p12 & 67.80s &{\bf 21.43s} &{\bf 21.43s} &38.23s \\
p13 & 59.60s &27.74s &27.74s &{\bf 13.16s} \\
p14 & 118.90s &54.71s &54.71s &{\bf 52.69s} \\
p15 & 62.30s &{\bf 43.49s} &{\bf 43.49s} &44.31s \\
p16 & 78.10s &{\bf 27.41s} &{\bf 27.41s} &45.84s \\
p17 & 45.90s &{\bf 27.73s} &{\bf 27.73s} &46.63s \\
p18 & 34.70s &{\bf 5.55s} &{\bf 5.55s} &15.63s \\
p19 & {\bf 108.40s} &- &- &- \\
p20 & {\bf 28.30s} &- &- &- \\
p21 & {\bf 279.00s} &- &- &- \\
p22 & {\bf 1668.00s} &- &- &- \\
p23 & {\bf 224.90s} &- &- &- \\
p24 & {\bf 2778.70s} &- &- &- \\
\end{tabular}

>>>>

\paragraph{Outline} We give details of our new algorithm in
Sec.~\ref{sec:algorithm}.  We use a fragment of the C programming lanugage
as our underlying logic, which is elaborated in Sec.~\ref{sec:logic}. We
summarize the results of our experiments in Sec.~\ref{sec:experiments}.

@@

\section{C-}
\label{sec:logic}

We use a fragment of C as our underlying logic.  We will refer to this fragment
as C-.  The characteristic property of C- is that safety can be decided for
C- programs by using a bounded model checker.  A C- program is just a C program
with the following syntactic restrictions:

@@

\section{Experimental Results}
\label{sec:experiments}

@@

\begin{figure}
\begin{center}
\begin{tabular}{l|r@{\,\,}|r@{\,\,}|r@{\,\,}|r@{\,\,}}
Problem & {\sc Brahma} & {\sc Kalashnikov} & {\sc Kalashnikov} & {\sc Kalashnikov} \\
        &               &                    & (no width)         & (CBMC only) \\
\hline
p1 & 3.20s &{\bf 1.83s} &23.54s &8.07s \\
p2 & 3.60s &{\bf 1.49s} &1271.12s &8.19s \\
p3 & {\bf 1.40s} &1.60s &4.09s &5.90s \\
p4 & 3.30s &{\bf 1.86s} &79.72s &8.15s \\
p5 & 2.20s &{\bf 1.98s} &12.16s &8.10s \\
p6 & 2.40s &{\bf 1.51s} &104.19s &8.17s \\
p7 & {\bf 1.00s} &4.04s &- &14.49s \\
p8 & {\bf 1.40s} &4.31s &- &14.20s \\
p9 & {\bf 5.80s} &35.09s &505.10s &13.45s \\
p10 & 76.10s &{\bf 9.80s} &- &19.14s \\
p11 & 57.10s &{\bf 9.40s} &{\bf 9.40s} &32.98s \\
p12 & 67.80s &{\bf 21.43s} &{\bf 21.43s} &38.23s \\
p13 & 59.60s &27.74s &27.74s &{\bf 13.16s} \\
p14 & 118.90s &54.71s &54.71s &{\bf 52.69s} \\
p15 & 62.30s &{\bf 43.49s} &{\bf 43.49s} &44.31s \\
p16 & 78.10s &{\bf 27.41s} &{\bf 27.41s} &45.84s \\
p17 & 45.90s &{\bf 27.73s} &{\bf 27.73s} &46.63s \\
p18 & 34.70s &{\bf 5.55s} &{\bf 5.55s} &15.63s \\
p19 & {\bf 108.40s} &-- &-- &-- \\
p20 & {\bf 28.30s} &-- &-- &-- \\
p21 & {\bf 279.00s} &-- &-- &-- \\
p22 & {\bf 1668.00s} &-- &-- &-- \\
p23 & {\bf 224.90s} &-- &-- &-- \\
p24 & {\bf 2778.70s} &-- &-- &-- \\
\end{tabular}
